Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-06 Paper.tex
Uncommenting \usepackage[utf8]{inputenc} again
It's perplexing that there is a difference between my local build and the repo Travis CI build, even though I have TeXLive installed.
grammar difficulty

This mechanism enforces a homeostasis in terms of the time between blocks; a smaller period between the last two blocks results in an increase in the difficulty level and thus additional computation required, lengthening the likely next period. Conversely, if the period is too large, the difficulty, and expected time to the next block, is reduced.

>>>>

This mechanism enforces a homeostasis in terms of the time between blocks; a smaller period between the last two blocks results in an increase in the difficulty level and thus additional computation is required, lengthening the likely next period. Conversely, if the period is too large, the difficulty, and expected time to the next block, is reduced.
